cardinalR: Generating interesting high-dimensional data structures

### 2025-05-01 paper-cardinalR.Rmd
Added initial projection for branches

```{r data-expbranches}
expbranches <- gen_expbranches(n = 1000, p = 4, k = 4)
```

@@

>>>>

```{r data-expbranches, echo=TRUE}
expbranches <- gen_expbranches(n = 1000, p = 4, k = 4)
```

@@

```{r expbranches-proj1}
scaled_data <- scale_data_manual(expbranches)

expbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r expbranches-proj2}

expbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r expbranches-proj3}

expbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-expbranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` data."}
#| fig-width: 15
#| fig-height: 5

expbranches_proj1 + expbranches_proj2 + expbranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-linearbranches, echo=TRUE}
linearbranches <- gen_linearbranches(n = 1000, p = 4, k = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(linearbranches)
```

```{r linearbranches-proj1}
scaled_data <- scale_data_manual(linearbranches)

linearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r linearbranches-proj2}

linearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r linearbranches-proj3}

linearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-linearbranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `linearbranches` data."}
#| fig-width: 15
#| fig-height: 5

linearbranches_proj1 + linearbranches_proj2 + linearbranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-curvybranches, echo=TRUE}
curvybranches <- gen_curvybranches(n = 1000, p = 4, k = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(curvybranches)
```

```{r curvybranches-proj1}
scaled_data <- scale_data_manual(curvybranches)

curvybranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r curvybranches-proj2}

curvybranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r curvybranches-proj3}

curvybranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-curvybranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvybranches` data."}
#| fig-width: 15
#| fig-height: 5

curvybranches_proj1 + curvybranches_proj2 + curvybranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-orglinearbranches, echo=TRUE}
orglinearbranches <- gen_orglinearbranches(n = 1000, p = 4, k = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(orglinearbranches)
```

```{r orglinearbranches-proj1}
scaled_data <- scale_data_manual(orglinearbranches)

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r orglinearbranches-proj2}

orglinearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r orglinearbranches-proj3}

orglinearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-orglinearbranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `orglinearbranches` data."}
#| fig-width: 15
#| fig-height: 5

orglinearbranches_proj1 + orglinearbranches_proj2 + orglinearbranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-orgcurvybranches, echo=TRUE}
orgcurvybranches <- gen_orgcurvybranches(n = 1000, p = 4, k = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(orgcurvybranches)
```

```{r orgcurvybranches-proj1}
scaled_data <- scale_data_manual(orgcurvybranches)

orgcurvybranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r orgcurvybranches-proj2}

orgcurvybranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r orgcurvybranches-proj3}

orgcurvybranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-orgcurvybranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `orgcurvybranches` data."}
#| fig-width: 15
#| fig-height: 5

orgcurvybranches_proj1 + orgcurvybranches_proj2 + orgcurvybranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
